### 2025-04-18 base-rates.qmd
20250418 - figure captions

```{r}
rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  psych::describe()

@@

@@

@@

>>>>

```{r}
rookiesDraftedEarly %>% 
  filter(position == "QB") %>%
  select(fantasyPoints) %>% 
  psych::describe()
```

```{r}
#| label: fig-histogramRookieQBs
#| fig-cap: "Histogram of Fantasy Points Among Rookie Quarterbacks Who Were Drafted in the First Two Rounds of the National Football League Draft."
#| fig-alt: "Histogram of Fantasy Points Among Rookie Quarterbacks Who Were Drafted in the First Two Rounds of the National Football League Draft."

@@

```{r}
#| label: fig-histogramRookieRBs
#| fig-cap: "Histogram of Fantasy Points Among Rookie Running Backs Who Were Drafted in the First Two Rounds of the National Football League Draft."
#| fig-alt: "Histogram of Fantasy Points Among Rookie Running Backs Who Were Drafted in the First Two Rounds of the National Football League Draft."

rookiesDraftedEarly %>% 
  filter(position == "RB") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

```{r}
#| label: fig-histogramRookieWRs
#| fig-cap: "Histogram of Fantasy Points Among Rookie Wide Receivers Who Were Drafted in the First Two Rounds of the National Football League Draft."
#| fig-alt: "Histogram of Fantasy Points Among Rookie Wide Receivers Who Were Drafted in the First Two Rounds of the National Football League Draft."

rookiesDraftedEarly %>% 
  filter(position == "WR") %>%
  select(fantasyPoints) %>% 
  hist()
```

@@

```{r}
#| label: fig-histogramRookieTEs
#| fig-cap: "Histogram of Fantasy Points Among Rookie Tight Ends Who Were Drafted in the First Two Rounds of the National Football League Draft."
#| fig-alt: "Histogram of Fantasy Points Among Rookie Tight Ends Who Were Drafted in the First Two Rounds of the National Football League Draft."

rookiesDraftedEarly %>% 
  filter(position == "TE") %>%
  select(fantasyPoints) %>% 
  hist()
```
